---
title: "Hi, My name is Susan"
author: "Susan Vanderplas"
date: "10/18/2020"
header-includes:
  - \usepackage{media9}
output: 
  beamer_presentation: 
    keep_tex: true
    colortheme: beaver
    fonttheme: professionalfonts
    theme: Boadilla
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
```


## Introduction

- Birthday: August 21
- I grew up in Houston, TX (for the most part)
- I got my undergrad degree in psychology and applied mathematical sciences
- I started my PhD in Bioinformatics before deciding that I hate plants (mostly, pollen) and don't want to help them achieve any sort of reproductive success

## Favorite Animal = Anything adorable and fuzzy

\includemedia[width=0.6\linewidth,height=0.6\linewidth,activate=pageopen,
passcontext,
transparent,
addresource=figure/otterlyAdorable.mp4,
flashvars={source=figure/otterlyAdorable.mp4}
]{\includegraphics[width=0.6\linewidth]{figure/Otters}}{figure/otterlyAdorable.mp4}

(This is a video if you open it with the right pdf reader)

## Favorite Plot

Ok, this isn't my favorite plot, but it is at least one that is fun and easy to generate...

```{r}
library(tidyverse)
tibble(x = seq(0, 2*pi, pi/24),
       y = sin(x),
       ymin = y - .25,
       ymax = y + .25) %>%
  ggplot(aes(x = x, xend = x, y = ymin, yend = ymax)) + geom_segment() +
  coord_fixed()

```

## CV

My CV can be found [here](https://github.com/srvanderplas/CV/raw/master/SusanVanderplas-CV.pdf)
