---
title: "Slidy: Hello, my name is Susan"
author: "Susan Vanderplas"
date: "10/18/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
```

## Introduction

- Birthday: August 21
- I grew up in Houston, TX (for the most part)
- I got my undergrad degree in psychology and applied mathematical sciences
- I started my PhD in Bioinformatics before deciding that I hate plants (mostly, pollen) and don't want to help them achieve any sort of reproductive success

## Favorite Animal = Anything adorable and fuzzy

<video width="240px" height = "320px" controls>
<source src="../md-beamer/figure/otterlyAdorable.mp4" type="video/mp4"/>
</video>

## Favorite Plot

Ok, this isn't my favorite plot, but it is at least one that is fun and easy to generate...

```{r}
library(tidyverse)
tibble(x = seq(0, 2*pi, pi/24),
       y = sin(x),
       ymin = y - .25,
       ymax = y + .25) %>%
  ggplot(aes(x = x, xend = x, y = ymin, yend = ymax)) + geom_segment() +
  coord_fixed()

```

## CV

My CV can be found [here](https://github.com/srvanderplas/CV/raw/master/SusanVanderplas-CV.pdf)


The CV I created for this assignment is [here](https://github.com/stat850-unl/10-presentation-srvanderplas/raw/master/CV/index.pdf)

